### 2012-06-21 inst/examples/criticaltransition.Rmd
critical transition examples

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
orig = getOption("device")
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
````

@@

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

@@

Now we'll simulate 100 replicates of this stochastic process, but with the system dynamics gradually changing over time.   
The bifurcation parameter will increase from `r pars[3]` to `r pars[3] + 2`.

``` {r simulationfunction}
ForwardSimulate <- 
  function(f, pars, x_grid, h_grid, x0, D, z_g,
         z_m=function(x) 1, z_i = function(x) 1, 
         profit=NULL){

@@

    # Move towards collapse
    pars[3] <- pars[3] + 2/OptTime

@@

@@

``` {r cleanup, echo=FALSE, include=FALSE}
options(device='orig')
````

>>>>

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 200
sigma_g <- .5
````

@@

``` {r  find_dp_opt }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=OptTime, xT=xT, 
                     profit, delta=delta, reward=0)
````

@@

Now we'll simulate 100 replicates of this stochastic process, but with the system dynamics gradually changing over time.

``` {r simulationfunction}
Dt <- 1

ForwardSimulate <- 
  function(f, pars, x_grid, h_grid, x0, D, z_g,
         z_m=function(x) 1, z_i = function(x) 1, 
         profit=NULL){

@@

    # Move towards collapse
    pars[3] <- pars[3] + Dt/OptTime

@@

The bifurcation parameter will increase from `r pars[3]` to `r pars[3] + Dt*(OptTime-1)/OptTime`.

@@
